Time Stretching of the GeV Emission of GRBs: Fermi LAT data vs geometrical model \\ {\large \url{https://github.com/maxitg/GammaRays}}

### 2014-08-27 Paper/gammaRays.tex
Fixed the number of energy bins in text to 300

Now, with basic filtering done, we can read events data from \texttt{timed.fits}. This file, however, contains observations of a large area of the sky.
Before using the data obtained from it, we should perform a more elaborate filtering by location using the point spread function of Fermi LAT, which can be computed with \texttt{gtpsf}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtpsf.txt}} tool.
We use 41 energy bins from \unit[100]{MeV} to \unit[300]{GeV}, and 300 angular bins with maximal angle being $30\degree$.
We use \texttt{gtltcube}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtltcube.txt}} tool to compute livetime maps, which are \texttt{gtpsf} need.
Note, that we need PSFs for all Instrument Response Functions of Fermi, that is for all event classes (transient, source, clean and ultraclean) and conversion types (back and front).

@@

The exposure map can be computed with the \texttt{gtexpcube2}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtexpcube2.txt}} tool. We compute it with 41 energy bins from \unit[100]{MeV} to \unit[300]{GeV}.

>>>>

Now, with basic filtering done, we can read events data from \texttt{timed.fits}. This file, however, contains observations of a large area of the sky.
Before using the data obtained from it, we should perform a more elaborate filtering by location using the point spread function of Fermi LAT, which can be computed with \texttt{gtpsf}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtpsf.txt}} tool.
We use 300 energy bins from \unit[100]{MeV} to \unit[300]{GeV}, and 300 angular bins with maximal angle being $30\degree$.
We use \texttt{gtltcube}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtltcube.txt}} tool to compute livetime maps, which are \texttt{gtpsf} need.
Note, that we need PSFs for all Instrument Response Functions of Fermi, that is for all event classes (transient, source, clean and ultraclean) and conversion types (back and front).

@@

The exposure map can be computed with the \texttt{gtexpcube2}\footnote{\url{http://fermi.gsfc.nasa.gov/ssc/data/analysis/scitools/help/gtexpcube2.txt}} tool. We compute it with 300 energy bins from \unit[100]{MeV} to \unit[300]{GeV}.
